Unknown

### 2024-04-08 ms/ms.qmd
added draft of tbl-parameters

1. Estimate \agcurve{} curve parameters for each leaf
2. Estimate \aax{} for each light intensity with leaf using \agcurve{} curve parameters
3. Estimate the effects of light intensity, light treatment, and accession on \aax{} (assimilatory and plasticity hypotheses)
4. Estimate the effects of native light habitat on accession-level \aax{} (constitutive hypothesis)

@@

@@

We tested for effects of light intensity, light treatment, accession, and their interactions on \aax. All models included effects of light intensity and light treatment, as well as random effects of accession and replicate within accession. More complex models included interactions between light intensity and light treatment, as well as random effects of accession on the effects of light intensity and light treatment. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ for fixed effects light intensity and treatment. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ for the the random effect standard deviation of replicate within accession. We accounted for the phylogenetic structure among the random effects of accession using an Ornstein-Uhlenbeck (OU) process [@hansen_stabilizing_1997]. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ on OU parameters. We modeled the residual standard deviation on a log-link scale with effects of light intensity and light treatment. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ on the residual standard deviation intercept and a weakly informative normal prior with mean $0$ and standard deviation $1$ on the effects of light intensity and light treatment on the residual standard deviation.

>>>>

1. Estimate \agcurve{} curve parameters
2. Estimate \aax{} for each light intensity with leaf using \agcurve{} curve parameters
3. Estimate the effects of light intensity, light treatment, and accession on \aax{} (assimilatory and plasticity hypotheses)
4. Estimate the effects of native light habitat on accession-level \aax{} (constitutive hypothesis)

@@

```{r, parameters, echo=FALSE,message=FALSE,warning=FALSE}
#| label: tbl-parameters
#| tbl-cap: "Description of parameters estimated in the hierarchical Bayesian model. The `Parameter` column lists the parameter name as it appears in text. The `Description` column provides a brief description of the parameter."

df_parameters = read_csv("../data/parameters1.csv", col_types = "ccccl") |>
    dplyr::filter(include)

df_parameters |>
  dplyr::select(Parameter = latex, Description = description) |>
  knitr::kable(
    format = "latex",
    align = c("l", "l"),
    booktabs = TRUE,
    escape = FALSE,
    longtable = TRUE
  ) |>
  kableExtra::kable_styling(latex_options = c("striped", "no_vertical_lines")) |>
  kableExtra::column_spec(1, width = "1in") |>
  kableExtra::column_spec(2, width = "5in") |>
  kableExtra::pack_rows("\\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "ags")),
                        max(which(df_parameters$par_type == "ags")),
                        escape = FALSE) |>
  kableExtra::pack_rows("\\aax{} for each light intensity with leaf using \\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "aa_est")),
                        max(which(df_parameters$par_type == "aa_est")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects light intensity, light treatments, and accession on \\aax",
                        min(which(df_parameters$par_type == "aa")),
                        max(which(df_parameters$par_type == "aa")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects of native light habitat on accession-level \\aax",
                        min(which(df_parameters$par_type == "ppfd_aa")),
                        max(which(df_parameters$par_type == "ppfd_aa")),
                        escape = FALSE)

@@

We tested for effects of light intensity, light treatment, accession, and their interactions on \aax. All models included effects of light intensity and light treatment, as well as random effects of accession and replicate within accession. More complex models included interactions between light intensity and light treatment, as well as random effects of accession on the effects of light intensity and light treatment. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ for fixed effects light intensity and treatment. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ for the the random effect standard deviation of replicate within accession. We accounted for the phylogenetic structure among the random effects of accession using an Ornstein-Uhlenbeck (OU) process [@hansen_stabilizing_1997]. The expected covariance between accessions $i$ and $j$ ($\text{Cov}(i, j)$ ) is:

$$\text{Cov}(i, j) = \frac{\sigma^2}{2 \alpha} \exp(-\alpha D_{ij})$$
where $\sigma^2$ is the variance of the random effect, $\alpha$ is the rate of decay of the covariance with phylogenetic distance, $D_{ij}$, the phylogenetic distance between accessions $i$ and $j$. We estimated $\sigma^2 / (2 \alpha)$ and $\alpha$ as a separate parameters and reparameterized them as $\sigma^2$ and $\alpha$. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ on OU parameters.

We modeled the residual standard deviation of \aax, (i.e. phylogenetically unstructured variation unaccounted for by explanatory variables) on a log-link scale with effects of light intensity and light treatment. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ on the residual standard deviation intercept and a weakly informative normal prior with mean $0$ and standard deviation $1$ on the effects of light intensity and light treatment on the residual standard deviation.

### 2024-04-08 ms/ms.tex
added draft of tbl-parameters

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Estimate \agcurve{} curve parameters for each leaf
\item
  Estimate \aax{} for each light intensity with leaf using \agcurve{}
  curve parameters
\item
  Estimate the effects of light intensity, light treatment, and
  accession on \aax{} (assimilatory and plasticity hypotheses)
\item
  Estimate the effects of native light habitat on accession-level \aax{}
  (constitutive hypothesis)
\end{enumerate}

@@

@@

Within the \(k^{\text{th}}\) leaf, we estimated \aax{} for each light
intensity by integrating the difference in \logA between the amphi and
pseudohypo \agcurve{} curves over the range of \gsw{} values where the
curves overlap. We used the following equation to estimate \aax{} for
the \(k^{\text{th}}\) leaf at light intensity \(l\) in accession \(m\):

@@

\[\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.\]
The function \(f : \Theta_1 \rightarrow \Theta_2\) maps the set
\(\Theta_1\) indexed by leaf type (amphi or pseudohypo), leaf replicate,
light intensity, and accession to set \(\Theta_2\) indexed by \agcurve{}
curve.

WORKING HERE

@@

Base model (need to add indices):

\[\text{log(A)} = \beta_0 + \beta_1 \text{log}(g_\text{sw}) + \beta_2 \text{log}(g_\text{sw}) ^ 2 + \epsilon\]
Estimate \aax{} by integrating over range of \gsw{} overlap (need to add
indices for accession, replicate, light intensity):

where \(\text{min(log(}g_\text{sw}))\) and
\(\text{max(log(}g_\text{sw}))\) are the minimum and maximum values of
\(\text{log(}g_\text{sw})\) where amphi and pseudohypo curves overlap.
\Aamphi{} is calculated from parameter estimates
\(\theta_\text{amphi} \in \{\beta_{0,\text{amphi}}, \beta_{1,\text{amphi}}, \beta_{2,\text{amphi}}\}\);
\Ahypo{} is calculated from parameter estimates
\(\theta_\text{hypo} \in \{\beta_{0,\text{hypo}}, \beta_{1,\text{hypo}}, \beta_{2,\text{hypo}}\}\)
for each curve.

>>>>

\begin{verbatim}

Attaching package: 'dplyr'
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:stats':

    filter, lag
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:base':

    intersect, setdiff, setequal, union
\end{verbatim}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Estimate \agcurve{} curve parameters
\item
  Estimate \aax{} for each light intensity with leaf using \agcurve{}
  curve parameters
\item
  Estimate the effects of light intensity, light treatment, and
  accession on \aax{} (assimilatory and plasticity hypotheses)
\item
  Estimate the effects of native light habitat on accession-level \aax{}
  (constitutive hypothesis)
\end{enumerate}

@@

\begin{longtable}{>{\raggedright\arraybackslash}p{1in}>{\raggedright\arraybackslash}p{5in}}

\caption{\label{tbl-parameters}Description of parameters estimated in
the hierarchical Bayesian model. The \texttt{Parameter} column lists the
parameter name as it appears in text. The \texttt{Description} column
provides a brief description of the parameter.}

\tabularnewline

\toprule
Parameter & Description\\
\midrule
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{\agcurve{} curve parameters}}\\
\hspace{1em}\cellcolor{gray!10}{$\mathbf{B}_\text{curve}$} & \cellcolor{gray!10}{$n_\text{curve} \times 3$ array of random \agcurve{} curve-level coefficients ($b_{0,j}$, $b_{1,j}$, $b_{2,j}$); $\mathbf{B}_\text{curve} \sim \text{MVN}(\vec{0}, \symbf{\Sigma}_\text{curve})$}\\
\hspace{1em}$\vec{\beta}_\text{curve}$ & vector of mean quadratic coefficients ($\beta_0$, $\beta_1$, $\beta_2$)\\
\hspace{1em}\cellcolor{gray!10}{$\symbf{\Sigma}_\text{curve}$} & \cellcolor{gray!10}{$3 \times 3$ covariance matrix of curve-level coefficients}\\
\hspace{1em}$\sigma_{\qty{6}{\raiseto{2}\centi\meter},\epsilon}$ & minimum residual standard deviation when the measured leaf surface area is $\qty{6}{\raiseto{2}\centi\meter}$\\
\hspace{1em}\cellcolor{gray!10}{$\beta_{S,\epsilon}$} & \cellcolor{gray!10}{slope of the relationship between residual standard deviation and measured leaf surface area (log-link scale)}\\
\hspace{1em}$\rho_{\epsilon}$ & lag-1 residual autocorrelation\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{\aax{} for each light intensity with leaf using agcurve{} curve parameters}}\\
\hspace{1em}\cellcolor{gray!10}{$\widehat{\mathrm{AA}}_{klm}$} & \cellcolor{gray!10}{estimate of \aax{} for the $k^{\text{th}}$ leaf at light intensity $l$ in accession $m$}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{effects light intensity, light treatments, and accession on \aax}}\\
\hspace{1em}$\beta_{\mathrm{AA},0}$ & intercept of \aax{} at low light intensity in shade treatment\\
\hspace{1em}\cellcolor{gray!10}{$\beta_{\mathrm{AA},2000}$} & \cellcolor{gray!10}{effect of high light intensity at \ppfdequals{2000} on \aax}\\
\hspace{1em}$\beta_{\mathrm{AA},\text{sun}}$ & effect of sun treatment on \aax{}\\
\hspace{1em}\cellcolor{gray!10}{$\beta_{\mathrm{AA},\text{2000,high}}$} & \cellcolor{gray!10}{effect of high light intensity at \ppfdequals{2000} on \aax{} in sun treatment}\\
\hspace{1em}$\vec{\beta}_{\mathrm{AA},\text{acc}}$ & vector of $n_\text{acc}$ phylogenetically structured random accession-level effects on \aax; $\vec{\beta}_{\mathrm{AA},\text{acc}} \sim \text{MVN}(\vec{0}, \symbf{\Sigma}_{\text{AA,acc}})$\\
\hspace{1em}\cellcolor{gray!10}{$\symbf{\Sigma}_{\text{AA,acc}}$} & \cellcolor{gray!10}{$n_\text{acc} \times n_\text{acc}$ covariance matrix of phylogenetically structured random accession-level effects on \aax;}\\
\hspace{1em}$\vec{\beta}_{\mathrm{AA},\text{rep}}$ & vector of $n_\text{rep}$ random replicate-level effects on \aax; $\vec{\beta}_{\mathrm{AA},\text{rep}} \sim \text{Normal}(0, \sigma_{\mathrm{AA},\text{rep}})$\\
\hspace{1em}\cellcolor{gray!10}{$\vec{\beta}_{\mathrm{AA},\text{2000,acc}}$} & \cellcolor{gray!10}{vector of $n_\text{acc}$ phylogenetically structured random accession-level effects of high light intensity at \ppfdequals{2000} on \aax; $\vec{\beta}_{\mathrm{AA},\text{2000,acc}} \sim \text{MVN}(\vec{0}, \symbf{\Sigma}_{\mathrm{AA},\text{2000,acc}})$}\\
\hspace{1em}$\vec{\beta}_{\mathrm{AA},\text{sun,acc}}$ & vector of $n_\text{acc}$ phylogenetically structured random accession-level effects of sun treatment on \aax; $\vec{\beta}_{\mathrm{AA},\text{sun,acc}} \sim \text{MVN}(\vec{0}, \symbf{\Sigma}_{\mathrm{AA},\text{sun,acc}})$\\
\hspace{1em}\cellcolor{gray!10}{$\sigma_{\mathrm{AA},\epsilon,0}$} & \cellcolor{gray!10}{intercept of phylogenetically unstructured residual standard deviation of \aax}\\
\hspace{1em}$\beta_{\mathrm{AA},\epsilon,2000}$ & effect of high light intensity at \ppfdequals{2000} on phylogenetically unstructured residual standard deviation of \aax{} (log-link scale)\\
\hspace{1em}\cellcolor{gray!10}{$\beta_{\mathrm{AA},\epsilon,\text{sun}}$} & \cellcolor{gray!10}{effect of sun treatment on phylogenetically unstructured residual standard deviation of \aax{} (log-link scale)}\\
\hspace{1em}$\sigma_{\mathrm{AA},\text{rep}}$ & standard deviation of random replicate-level effects on \aax\\
\hspace{1em}\cellcolor{gray!10}{$\alpha_{\mathrm{AA},\text{acc}}$} & \cellcolor{gray!10}{decay rate of phylogenetic covariance in random accession-level effects on \aax}\\
\hspace{1em}$\sigma^2_{\mathrm{AA},\text{acc}}$ & phylogenetic diffusion rate in random accession-level effects on \aax\\
\hspace{1em}\cellcolor{gray!10}{$\alpha_{\mathrm{AA},\text{2000,acc}}$} & \cellcolor{gray!10}{decay rate of phylogenetic covariance in random accession-level effects of high light intensity at \ppfdequals{2000} on \aax}\\
\hspace{1em}$\sigma^2_{\mathrm{AA},\text{2000,acc}}$ & phylogenetic diffusion rate in random accession-level effects of high light intensity at \ppfdequals{2000} on \aax\\
\hspace{1em}\cellcolor{gray!10}{$\alpha_{\mathrm{AA},\text{sun,acc}}$} & \cellcolor{gray!10}{decay rate of phylogenetic covariance in random accession-level effects of sun treatment on \aax}\\
\hspace{1em}$\sigma^2_{\mathrm{AA},\text{sun,acc}}$ & phylogenetic diffusion rate in random accession-level effects of sun treatment on \aax\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{effects of native light habitat on accession-level \aax}}\\
\hspace{1em}\cellcolor{gray!10}{$\beta_{\mathrm{AA},\text{PPFD},0}$} & \cellcolor{gray!10}{intercept of accession-level \aax{} when native \ppfdequals{0}}\\
\hspace{1em}$\beta_{\mathrm{AA},\text{PPFD},1}$ & slope of native \ppfd{} on accession-level \aax{}\\
\bottomrule

\end{longtable}

@@

Within the \(k^{\text{th}}\) leaf, we estimated \aax{} for each light
intensity by integrating the difference in \logA between the amphi and
pseudohypo \agcurve{} curves over the range of \gsw{} values where the
curves overlap (from \(\min(\log(g_\text{sw}))\) to
\(\max(\log(g_\text{sw}))\)). The estimate of \aax{} for the
\(k^{\text{th}}\) leaf at light intensity \(l\) in accession \(m\) is:

@@

\[\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.\]
The function \(f : \Theta_1 \rightarrow \Theta_2\) maps the set
\(\Theta_1\) indexed by leaf type (amphi or pseudohypo), leaf replicate,
light intensity, and accession to set \(\Theta_2\) indexed by individual
\agcurve{} curve. This mapping is necessary because the random effects
structure differs between models of \loggsw on \logA and that of models
predicting \aax{} described in the next section.

\subparagraph{\texorpdfstring{Effects of light intensity, light
treatment, and accession on
\aax}{Effects of light intensity, light treatment, and accession on }}\label{effects-of-light-intensity-light-treatment-and-accession-on}

We tested for effects of light intensity, light treatment, accession,
and their interactions on \aax. All models included effects of light
intensity and light treatment, as well as random effects of accession
and replicate within accession. More complex models included
interactions between light intensity and light treatment, as well as
random effects of accession on the effects of light intensity and light
treatment. We used a weakly informative normal prior with mean \(0\) and
standard deviation \(10\) for fixed effects light intensity and
treatment. We used a weakly informative normal prior with mean \(-3\)
and standard deviation \(5\) for the the random effect standard
deviation of replicate within accession. We accounted for the
phylogenetic structure among the random effects of accession using an
Ornstein-Uhlenbeck (OU) process (\textbf{hansen\_stabilizing\_1997?}).
The expected covariance between accessions \(i\) and \(j\)
(\(\text{Cov}(i, j)\) ) is:

\[\text{Cov}(i, j) = \frac{\sigma^2}{2 \alpha} \exp(-\alpha D_{ij})\]
where \(\sigma^2\) is the variance of the random effect, \(\alpha\) is
the rate of decay of the covariance with phylogenetic distance,
\(D_{ij}\), the phylogenetic distance between accessions \(i\) and
\(j\). We estimated \(\sigma^2 / (2 \alpha)\) and \(\alpha\) as a
separate parameters and reparameterized them as \(\sigma^2\) and
\(\alpha\). We used a weakly informative normal prior with mean \(0\)
and standard deviation \(10\) on OU parameters.

We modeled the residual standard deviation of \aax,
(i.e.~phylogenetically unstructured variation unaccounted for by
explanatory variables) on a log-link scale with effects of light
intensity and light treatment. We used a weakly informative normal prior
with mean \(-3\) and standard deviation \(5\) on the residual standard
deviation intercept and a weakly informative normal prior with mean
\(0\) and standard deviation \(1\) on the effects of light intensity and
light treatment on the residual standard deviation.

\subparagraph{\texorpdfstring{Effects of native light habitat on
accession-level
\aax}{Effects of native light habitat on accession-level }}\label{effects-of-native-light-habitat-on-accession-level}

We tested a linear effect of native light habitat on accession-level
\aax. In Models 1 and 2, we used the random intercept of \aax{} as a
response variable; in model 3 we used the random intercept plus the
random effect of accession at high light intensity; in model 4 we used
the random intercept plus the random effect of accession in the sun
treatment; in model 5 we used the random intercept plus the random
effects of accession at high light intensity and sun treatment. We used
a weakly informative normal prior with mean \(0\) and standard deviation
\(1\) for the slope and intercept. We accounted for the phylogenetic
structure among the model residuals using an (OU) process. We used a
weakly informative normal prior with mean \(0\) and standard deviation
\(10\) on OU parameters.

WORKING HERE - TABLE OR SOMETHING SUMMARIZING MODELS? - TABLE
SUMMARIZING PARAMETERS

@@

### 2024-04-08 ms/test.qmd
added draft of tbl-parameters

df_parameters = read_csv("../data/parameters1.csv", col_types = "cccc", n_max = 6)

df_parameters |>
  dplyr::select(Parameter = latex, Description = description) |>
  knitr::kable(
    format = "latex",
    align = c("c", "l"),
    booktabs = TRUE,
    escape = FALSE
  ) |>
  kableExtra::kable_styling(latex_options = c("striped", "no_vertical_lines")) |>
  kableExtra::column_spec(1, width = "1in") |>
  kableExtra::column_spec(2, width = "5in") |>
  kableExtra::pack_rows("\\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "ags")),
                        max(which(df_parameters$par_type == "ags")),
                        escape = FALSE) #|>
                        # kableExtra::pack_rows("x", 2, 2)

>>>>

df_parameters = read_csv("../data/parameters1.csv", col_types = "ccccl") |>
    dplyr::filter(include)

df_parameters |>
  dplyr::select(Parameter = latex, Description = description) |>
  knitr::kable(
    format = "latex",
    align = c("l", "l"),
    booktabs = TRUE,
    escape = FALSE,
    longtable = TRUE
  ) |>
  kableExtra::kable_styling(latex_options = c("striped", "no_vertical_lines")) |>
  kableExtra::column_spec(1, width = "1in") |>
  kableExtra::column_spec(2, width = "5in") |>
  kableExtra::pack_rows("\\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "ags")),
                        max(which(df_parameters$par_type == "ags")),
                        escape = FALSE) |>
  kableExtra::pack_rows("\\aax{} for each light intensity with leaf using \\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "aa_est")),
                        max(which(df_parameters$par_type == "aa_est")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects light intensity, light treatments, and accession on \\aax",
                        min(which(df_parameters$par_type == "aa")),
                        max(which(df_parameters$par_type == "aa")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects of native light habitat on accession-level \\aax",
                        min(which(df_parameters$par_type == "ppfd_aa")),
                        max(which(df_parameters$par_type == "ppfd_aa")),
                        escape = FALSE)
